Self-similarity of the elements of the feasible set

### 2020-08-12 analysis/reports/self_similarity.Rmd
maybe run

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)
library(scadsanalysis)

@@

#### Walkthrough

```{r load net}

## Set up the cache and config
db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-net.sqlite"))
cache <- storr::storr_dbi("datatable", "keystable", db)
cache$del(key = "lock", namespace = "session")
knitr::opts_chunk$set(fig.width=3, fig.height=2.5, warning = FALSE, message = FALSE)

net_summary <- readd(all_di_summary, cache = cache)

net_summary <- net_summary %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)))

example_fs <- readd(fs_s_7_n_71, cache = cache)

example_di <- readd(di_fs_s_7_n_71, cache =cache)

example_fs <- example_fs %>%
  left_join(example_di) %>%
  left_join(net_summary)
```

Here we have a bank of `r length(unique(example_fs$sim))` samples from the feasible set for SADs with 7 species and 71 individuals.

```{r illustrate self similarity}

ggplot(example_fs, aes(x = rank, y = abund, group = sim)) +
  geom_line(alpha = .1) +
  theme_bw()
```

We draw two of these samples to compare.

```{r draw two}

set.seed(1977)

comparison <- fs_diff_sampler(example_fs)

sims <- c(comparison$sim1[1], comparison$sim2[1])

comparison_fs <- filter(example_fs, sim %in% sims) %>%
  mutate(sim = as.factor(sim))

ggplot(comparison_fs, aes(x = rank, y = abund, color = sim)) +
  geom_line() +
  geom_point() +
  theme_bw() +
  scale_color_viridis_d(end = .7)

```

I have implemented 5 metrics of similarity for comparing samples:

* R2
* R2 on log-transformed abundances
* The coefficient of determination from a linear model fitting one sample to the other
* The proportion of individuals allocated to species of differing abundances
* The estimated Kullbak-Lieber (sp) divergence between the two samples

```{r self similarity metrics}

comparison

```

We repeat this comparison process numerous times to get numerous values for the self-similarity metrics.

```{r rep sampler, fig.dim = c(3,3)}

comparisons <- rep_diff_sampler(example_fs, ndraws = 100)

nrow(
  comparisons %>%
    select(sim1, sim2) %>%
    distinct()
)

ggplot(comparisons, aes(r2)) +
  geom_density() +
  theme_bw()

ggplot(comparisons, aes(r2_log)) +
  geom_density() +
  theme_bw()

ggplot(comparisons, aes(cd)) +
  geom_density() +
  theme_bw()

ggplot(comparisons, aes(prop_off)) +
  geom_density() +
  theme_bw()

ggplot(comparisons, aes(div)) +
  geom_density() +
  theme_bw()
```

We repeat this process for feasible sets with varying S and N, and compare the distribution of the self-similarity metrics across the variation in S and N.
